Distributed Algorithms for Sparse Matrix-Vector Multiplication

### 2015-04-24 presentation.Rmd
Whew, more work

## Outline

## Introduction

@@

The goal is to minimize the function F, which is minimizing the **largest bucket size that yields the highest computing time**.

@@

## Third Paper

## The BRC (Blocked Row-Column) Format

## Model Parameters

## Results

## Results (Continued)

## Multiple GPUs

## Caveat: Pre-Processing Overhead

>>>>

## Outline
- Statistics Background
- Load Balanced Sparse Matrix-Multiplication
- Architecture-aware Technique
- Scalable Parallel Matrix Multiplication

@@

The goal is to minimize the function F, which is minimizing the **largest bucket size that yields the highest computing time**. Call this procedure GALA.

## Overview of Algorithm
<img src="images/alggg.png" width="800px">

## Communication
The broadcast operation can be quite expensive.

Hypercube and mesh topologies yield broadcast complexities of $O(log(P))$ and $O(\sqrt{P})$ respectively.

On the other hand, software pipelining enables a communications complexity of $O(1 + P/Q)$ per each vector, where P is the
number of processing elements and Q is the number of vectors. Note what happens when $Q >> P$...

@@

## Scalable Parallel Matrix Multiplication on Distributed Memory Parallel Computers

## Primary Result
For any $O(N^{\alpha})$ sequential matrix multiplication algorithm over an arbitrary ring with $2 < \alpha \le 3$, there is a fully scalable parallel implementation on Distributed Memory Parallel Computers (DMPC).

That is, for all $1 \le p \le N^{\alpha}/log(N)$, multiplying two $N \times N$ matrices can be performed by a DMPC with p processors in $O(N^{\alpha}/p)$ time, and linear speedup can be achieved in the
range $[1..N^{\alpha}/log(N)]$.

In particular, multiplying two $N \times N$ matrices can be performed in $O(log(N))$ time by a DMPC with $N^{\alpha}/log(N)$ processors. This matches the performance of PRAM.

## Distributed Memory Parallel Computers (DMPC)
<img src="images/dmpc.png" width="600px">

## Lemma 1 and Lemma 2
A processor group (a consecutive group of t processors) holding an $m^l \times m^l$ matrix $X$ can send $X$ to another processor group in one communication step.

Further, it can be sent to all processor groups in parallel in $log(R) + 1$ communication steps, where R is the number of processor groups. (A broadcast)

## The Recursive Algorithm
<img src="images/bil.png" width="500px">

## Step D
<img src="images/stepd.png" width="500px">

## Step C
<img src="images/stepc.png" width="500px">
